Covid-19 infection and attributable mortality in residents of UK care homes: Cohort study using electronic records (March-June 2020)

### 2020-07-12 manuscript/manuscript.Rmd
manuscript v1.0

---
title: "Covid-19 infection and attributable mortality in residents of UK care homes: Cohort study using electronic records (March-June 2020)"
# author: "Dutey-Magni, PF, Williams, H, Hayward, A, Shallcross, L"
bibliography: references.bib
csl: sage-vancouver.csl
output:
  word_document:
    toc: yes
    reference_docx: template.docx
  html_document:
    df_print: paged
    toc: yes
    code_folding: hide
link-citations: yes
always_allow_html: yes
---

@@

```{r fig_KM_CT_plots, fig.height = 4, fig.width = 12, message=FALSE}
write.csv(km_ct_residents_symp, file = "supp_table_kaplan_meier_residents_symptomatic.csv", row.names = F)
write.csv(km_ct_residents_confirmed, file = "supp_table_kaplan_meier_residents_confirmed.csv", row.names = F)
write.csv(km_ct_residents_deaths, file = "supp_table_kaplan_meier_residents_deaths.csv", row.names = F)

@@

km_residents_graph <- ggplot(aes(x = date, y = 1-S_t, 
           ymax = 1 - St_max,
           ymin = 1 - St_min,
           color = Event), data = all_km_residents) +
  geom_ribbon(alpha=0.1, linetype = 2 ) +
  geom_path(lwd=1.2) +
  geom_text(aes(label = if_else(
    date == get_monday_date(date),
    formatbm(round((1-S_t) * desc_residents$CT_total_residents)),
    ""
  )), position = position_nudge(y = .02)) +
  scale_y_continuous("Cumulative incidence",
                     breaks = seq(0,1,.02)) +
  ggsci::scale_color_lancet() +
  scale_x_date(name = "Date", 
               breaks = unique(get_monday_date(all_km_residents$date)),
               labels = format.Date(
                 unique(get_monday_date(all_km_residents$date)),
                 "%e %b %Y"
               )) +
  theme_bw()  +
  theme(axis.text.x = element_text(angle = 25, vjust = 1, hjust=1)) +
  coord_cartesian(ylim = c(0,0.27)) + ggtitle("(A) Residents")

all_km_staff <- bind_rows(
  km_staff_symptomatic,
  km_staff_confirmed
)
all_km_staff$Event <- factor(
  all_km_staff$event,
  levels = c(
    "Symptomatic case",
    "Confirmed infection"
  )
)
write.csv(km_staff_symptomatic, file = "supp_table_kaplan_meier_staff_symptomatic.csv", row.names = F)
write.csv(km_staff_confirmed, file = "supp_table_kaplan_meier_staff_confirmed.csv", row.names = F)

km_staff_graph <- ggplot(aes(x = date, y = 1-S_t, 
           ymax = 1 - St_max,
           ymin = 1 - St_min,
           color = Event), data = all_km_staff) +
  geom_ribbon(alpha=0.1, linetype = 2,stat = ) +
  geom_path(lwd=1.2) +
  geom_text(aes(label = if_else(
    date == get_monday_date(date),
    formatbm(round((1-S_t) * desc_staff$total_staff)),
    ""
  )), position = position_nudge(y = .02)) +
  ggsci::scale_color_lancet()+
  scale_y_continuous("Cumulative incidence",
                     breaks = seq(0,1,.02)) +
  scale_x_date(name = "Date", 
               breaks = unique(get_monday_date(km_staff_symptomatic$date)),
               labels = format.Date(
                 unique(get_monday_date(km_staff_symptomatic$date)),
                 "%e %b %Y"
               )) +
  theme_bw() +
  theme(legend.position = "none", 
        axis.text.x = element_text(angle = 25, vjust = 1, hjust=1)) +
  coord_cartesian(ylim = c(0,0.27)) +  ggtitle("(B) Staff")

@@

```{r tablefiller1, results="asis"}
arsenal::tableby(
  confirmed  ~ gender + ageg  +  home_type + user_type2 +bed_tot_category + bed_to_staff_ratio +  occ_bedroom_ratio_g6, 
  control = arsenal::tableby.control(test = FALSE, cat.stats = "countrowpct", digits = 1L),
  data = residents_overview) %>%  summary()

@@

```{r tablefiller2, results="asis"}
residents_overview$death_status <- as.integer(residents_overview$status == "Deceased")
arsenal::tableby(
  death_status  ~ gender + ageg  +  home_type + user_type2  + bed_to_staff_ratio + bed_tot_category +  occ_bedroom_ratio_g6 + covid_status_outbreak, 
  control = arsenal::tableby.control(test = FALSE, cat.stats = "countrowpct", digits = 1L),
  data = residents_overview) %>%  summary()

@@

KM_mortality_plot <- KM_mortality_plot +  
  scale_x_continuous(name = "Date", 
                     breaks = c(seq(0, 7*50, 7)),
                     labels = format.Date(date_min + seq(0, 7*50, 7), "%e %b %Y" )) +
  theme(axis.text.x = element_text(size = 8, angle = 35, vjust = 1, hjust=1)) 
pdf("figure3.pdf", 8, 6)
KM_mortality_plot
dev.off()
KM_mortality_plot
```

>>>>

---
title: "Covid-19 infection and attributable mortality in residents of UK care homes: Cohort study using electronic records (March-June 2020)"
bibliography: references.bib
csl: sage-vancouver.csl
output:
  html_document:
    df_print: paged
    toc: yes
    code_folding: hide
  word_document:
    toc: yes
    reference_docx: template.docx
link-citations: yes
always_allow_html: yes
---

@@

```{r fig_KM_CT_plots, fig.height = 4, fig.width = 12, message=FALSE}

km_ct_residents_symp$y <- (1-km_ct_residents_symp$S_t) * desc_residents$CT_total_residents
km_ct_residents_confirmed$y <- (1-km_ct_residents_confirmed$S_t) * desc_residents$CT_total_residents
km_ct_residents_deaths$y <- (1-km_ct_residents_deaths$S_t) * desc_residents$CT_total_residents

write.csv(km_ct_residents_symp, file = "supp_table_kaplan_meier_residents_symptomatic.csv", row.names = F)
write.csv(km_ct_residents_confirmed, file = "supp_table_kaplan_meier_residents_confirmed.csv", row.names = F)
write.csv(km_ct_residents_deaths, file = "supp_table_kaplan_meier_residents_deaths.csv", row.names = F)

@@

km_residents_graph <- ggplot(aes(x = date, y = 1-S_t, 
           ymax = 1 - St_max,
           ymin = 1 - St_min,
           color = Event), data = all_km_residents) +
  geom_ribbon(alpha=0.1, linetype = 2 ) +
  geom_path(lwd=1.2) +
  geom_text(aes(label = if_else(
    date == get_monday_date(date),
    formatbm(round((1-S_t) * desc_residents$CT_total_residents)),
    ""
  )), size = 3, position = position_nudge(y = .02)) +
  scale_y_continuous("Cumulative incidence",
                     breaks = seq(0,1,.02)) +
  ggsci::scale_color_lancet() +
  scale_x_date(name = "Date", 
               breaks = unique(get_monday_date(all_km_residents$date)),
               labels = format.Date(
                 unique(get_monday_date(all_km_residents$date)),
                 "%e %b %Y"
               )) +
  theme_bw()  +
  theme(axis.text.x = element_text(angle = 25, vjust = 1, hjust=1)) +
  coord_cartesian(ylim = c(0,0.27)) + ggtitle("(A) Residents")

all_km_staff <- bind_rows(
  km_staff_symptomatic,
  km_staff_confirmed
)
all_km_staff$Event <- factor(
  all_km_staff$event,
  levels = c(
    "Symptomatic case",
    "Confirmed infection"
  )
)

km_staff_symptomatic$y <- (1-km_staff_symptomatic$S_t) * desc_staff$total_staff
km_staff_confirmed$y <- (1-km_staff_confirmed$S_t) * desc_staff$total_staff
write.csv(km_staff_symptomatic, file = "supp_table_kaplan_meier_staff_symptomatic.csv", row.names = F)
write.csv(km_staff_confirmed, file = "supp_table_kaplan_meier_staff_confirmed.csv", row.names = F)

km_staff_graph <- ggplot(aes(x = date, y = 1-S_t, 
           ymax = 1 - St_max,
           ymin = 1 - St_min,
           color = Event), data = all_km_staff) +
  geom_ribbon(alpha=0.1, linetype = 2,stat = ) +
  geom_path(lwd=1.2) +
  geom_text(aes(label = if_else(
    date == get_monday_date(date),
    formatbm(round((1-S_t) * desc_staff$total_staff)),
    ""
  )), size = 3, position = position_nudge(y = .02)) +
  ggsci::scale_color_lancet()+
  scale_y_continuous("Cumulative incidence",
                     breaks = seq(0,1,.02)) +
  scale_x_date(name = "Date", 
               breaks = unique(get_monday_date(km_staff_symptomatic$date)),
               labels = format.Date(
                 unique(get_monday_date(km_staff_symptomatic$date)),
                 "%e %b %Y"
               )) +
  theme_bw() +
  theme(legend.position = "none", 
        axis.text.x = element_text(angle = 25, vjust = 1, hjust=1)) +
  coord_cartesian(ylim = c(0,0.27)) +  ggtitle("(B) Staff")

@@

```{r tablefiller1, results="asis"}
# arsenal::tableby(
#   confirmed  ~ gender + ageg  +  home_type + user_type2 +bed_tot_category + bed_to_staff_ratio +  occ_bedroom_ratio_g6, 
#   control = arsenal::tableby.control(test = FALSE, cat.stats = "countrowpct", digits = 1L),
#   data = residents_overview) %>%  summary()

@@

```{r tablefiller2, results="asis"}
# residents_overview$death_status <- as.integer(residents_overview$status == "Deceased")
# arsenal::tableby(
#   death_status  ~ gender + ageg  +  home_type + user_type2  + bed_to_staff_ratio + bed_tot_category +  occ_bedroom_ratio_g6 + covid_status_outbreak, 
#   control = arsenal::tableby.control(test = FALSE, cat.stats = "countrowpct", digits = 1L),
#   data = residents_overview) %>%  summary()

@@

KM_mortality_plot <- KM_mortality_plot +  
  scale_x_continuous(name = "Date", 
                     breaks = c(seq(0, 7*50, 7)),
                     labels = format.Date(date_min + seq(0, 7*50, 7), "%e %b %Y" )) +
  theme(axis.text.x = element_text(size = 8, angle = 35, vjust = 1, hjust=1)) 
pdf("figure3.pdf", 8, 6)
KM_mortality_plot
dev.off()
KM_mortality_plot

summary(KM_mortality_by_covid_status)[c("time",  "n.risk", "n.event", "n.censor", "surv", "strata")] %>% 
  as_tibble %>% 
  mutate(infection = gsub("covid_status=", "", gsub(", outbreak=.*", "", strata)),
         outbreak = gsub(".*, outbreak=", "", strata))  %>% 
  select(-strata) %>% 
  write.csv(file = "supp_table_kaplan_meier_indiv_alldeaths.csv", row.names = F)
```
